07_DESeq_ALL

### 2019-04-25 analysis/01_DESeq2.Rmd
parallel but not fast enough yet

@@

```{r dds}
dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = samples,
                              design = ~ treatment * sex * tissue )

dds <- dds[ rowSums(counts(dds)) > 10, ] ## pre-filter genes 
dds <- DESeq(dds) # Differential expression analysis
```

>>>>

library("BiocParallel")
register(MulticoreParam(4))

@@

```{r dds}
dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = samples,
                              design = ~ sex * tissue * treatment )

dds <- estimateSizeFactors(dds)
dds

# here filtering on moderate counts in 10 samples out of totla
nsamp <- 24
keep <- rowSums(counts(dds, normalized=TRUE) >= 10) >= nsamp
table(keep)

dds <- dds[keep,] 
dds

dds <- DESeq(dds, parallel = TRUE) # Differential expression analysis
```
